Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?

### 2024-09-08 slides/slides.tex
update slides

\author[Bohan Zhang]{Bohan Zhang$^{1}$, Anastasios Panagiotelis$^{2}$, and Han Li$^{3}$} % Your name
	\institute[] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
	%{\small {$^1$ \small  Department of Statistics and Department of Mathematics\\ \textbf{Purdue University}}\\ 
	 %\vskip 0.2cm	
  	{\small {$^1$ \small School of Economics and Management, Beihang University}
   \vskip 0.2cm
	\small {$^2$ Discipline of Business Analytics, Business School, University of Sydney}	
    \vskip 0.2cm
  	\small {$^3$ \small Centre for Actuarial Studies, Department of Economics, University of Melbourne}
   \vskip 0.5cm
\textbf{The 44th International Symposium on Forecasting, Dijon, France}
}
	\date{30 June - 3 July, 2024} % Date, can be changed to a custom date

@@

	\begin{itemize}
		\item Forecast reconciliation can be interpreted from the forecast combination perspective (\citealp{hollymanUnderstandingForecastReconciliation2021,difonzoForecastCombinationbasedForecast2024}).
		\item Reconciled forecasts are weighted combination of ``direct'' and ``indirect'' base forecasts. 
		\[
			\tilde{y}_{AA} = w_1 \hat y_{AA} + w_2 (\hat y_{A} -\hat y_{AB}) + w_3 (\hat y_{Total} - \hat y_{AB} - \hat y_{BA} - \hat y_{BB})
		\]

@@

\begin{frame}{Research questions}
	\begin{researchquestion}
		In terms of forecast performance, can {\color{red} the use of middle level series lead to improvement} compared to a two-level hierarchy (consisting of only top and bottom time series)? If so, is it possible to {\color{red} construct hierarchies in a data-driven way} that leads to further improvements in forecast accuracy?
	\end{researchquestion}

@@

\begin{frame}{Time series clustering-based forecast reconciliation}
	To the best of our knowledge, four studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.

@@

	The time series representation refers to the object that acts as an input for time series clustering. We consider four representations:
	\begin{itemize}
		\item {\color{red} Raw time series}.
		\item {\color{red} In-sample one-step-ahead forecast error}. A key step in MinT reconciliation is to estimate $\boldsymbol{W}_h$ based on in-sample forecast error.
		\item {\color{red} Time series features of raw time series}.
		\item {\color{red} Time series features of in-sample one-step-ahead forecast error}. 
		\begin{itemize}
			\item Features are low dimensional representation of time series, and have been used in various tasks such as clustering and forecasting.
			\item $56$ features calculated by the \texttt{tsfeatures} package in R are included.
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Australian tourism dataset}
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{../manuscript/figures/tourism.pdf}
	\end{figure}
	\begin{itemize}
		\item Monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016 (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
		\item Consists of $555$ time series with $304$ of those at the bottom level. The middle-level series are constructed based on state, region, city and travel purpose.
	\end{itemize}

@@

\begin{frame}{U.S. cause-of-death count dataset}
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{../manuscript/figures/mortality.pdf}
	\end{figure}
	\begin{itemize}
		\item Monthly cause-specific death count data of U.S. for the period between January 1999 and December 2019.
		\item Consists of $120$ time series, with $98$ of those being bottom-level series. The middle-level series are constructed based on major cause-of-death groups.
	\end{itemize}
\end{frame}

@@

	\begin{figure}
		\centering
		\includegraphics[width=0.4\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P3_mcb_benchmarks_h12.pdf}
		\includegraphics[width=0.4\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P3_mcb_benchmarks_h12.pdf}
		\caption{Average ranks and 95\% confidence intervals for twelve cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on MCB test.}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=0.8\textwidth]{../manuscript/figures/aggcluster_random.pdf}
		\caption{Examples of a given hierarchy and its “twin”.}
	\end{figure}
\end{frame}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
	\caption{Average ranks and 95\% confidence intervals for natural hierarchy and its 100 twins, tourism dataset (left) and mortality dataset(right).}
\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
		\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
		\caption{Average ranks and 95\% confidence intervals for the best cluster hierarchy and its 100 twins, tourism dataset (left) and mortality dataset(right).}
	\end{figure}

@@

\begin{frame}{Forecast combination}
	\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P4_benchmarks_h12.pdf}
	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P4_benchmarks_h12.pdf}
	\caption{Average ranks and 95\% confidence intervals for all approaches on tourism dataset(left) and mortality dataset(right) based on MCB test}
	\end{figure}
	\begin{itemize}
		\item On both datasets, forecast combination improves forecast performance compared to any single hierarchy. The improvement on the mortality dataset is more pronounced.
	\end{itemize}
\end{frame}

@@

		\item[] \small\color{purple}Contact email: {\color{blue}   zhangbohan@buaa.edu.cn}

@@

\begin{frame}[noframenumbering]{References}
	\bibliographystyle{agsm}
	\bibliography{../manuscript/references.bib}		
\end{frame}

>>>>

\author[Bohan Zhang]{Bohan Zhang$^{1}$, Anastasios Panagiotelis$^{2}$, and Han Li$^{3}$} % Your name
	\institute[] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
	%{\small {$^1$ \small  Department of Statistics and Department of Mathematics\\ \textbf{Purdue University}}\\ 
	 %\vskip 0.2cm	
  	{\small {$^1$ \small School of Economics and Management, Beihang University}
   \vskip 0.2cm
	\small {$^2$ Discipline of Business Analytics, Business School, University of Sydney}	
    \vskip 0.2cm
  	\small {$^3$ \small Centre for Actuarial Studies, Department of Economics, University of Melbourne}
   \vskip 0.5cm
\textbf{The 44th International Symposium on Forecasting, Dijon, France}
}
	\date{3 July, 2024} % Date, can be changed to a custom date

@@

	\begin{itemize}
		\item Forecast reconciliation can be interpreted from the forecast combination perspective (\citealp{hollymanUnderstandingForecastReconciliation2021,di2024forecast}).
		\item Reconciled forecasts are weighted combination of ``direct'' and ``indirect'' base forecasts. 
		\[
			\tilde{y}_{AA} = w_1 \hat y_{AA} + w_2 (\hat y_{A} -\hat y_{AB}) + w_3 (\hat y_{Total} - \hat y_{AB} - \hat y_{BA} - \hat y_{BB})
		\]

@@

\begin{frame}{Research questions}
	\begin{researchquestion}
		In terms of forecast performance, can {\color{red} augmenting middle level series lead to improvement}? If so, is it possible to {\color{red} construct hierarchies in a data-driven way} that leads to further improvements in forecast accuracy?
	\end{researchquestion}

@@

\begin{frame}{Time series clustering-based forecast reconciliation}
	Some previous studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.

@@

	The time series representation refers to the object that acts as an input for time series clustering. We consider four representations:
	\begin{itemize}
		\item {Raw time series}.
		\item {In-sample one-step-ahead forecast error}. 
		\item {Time series features of raw time series}.
		\item {Time series features of in-sample one-step-ahead forecast error}.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Australian tourism dataset}
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{tourism.pdf}
	\end{figure}
	\begin{itemize}
		\item Monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016 (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
		\item Consists of $525$ unique time series with $304$ of those at the bottom level. The middle-level series are constructed based on state, region, city and travel purpose.
	\end{itemize}

@@

\begin{frame}{U.S. cause-of-death count dataset}
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{mortality.pdf}
	\end{figure}
	\begin{itemize}
		\item Monthly cause-specific death count data of U.S. for the period between January 1999 and December 2019.
		\item Consists of $120$ time series, with $98$ of those being bottom-level series. The middle-level series are constructed based on major cause-of-death groups.
	\end{itemize}
\end{frame}

@@

	\begin{figure}
		\centering
		\includegraphics[width=0.4\textwidth]{hierarchy_rmsse/tourism/P3_mcb_benchmarks_h12.pdf}
		\includegraphics[width=0.4\textwidth]{hierarchy_rmsse/mortality/P3_mcb_benchmarks_h12.pdf}
		\caption{Average ranks and 95\% confidence intervals for twelve cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on MCB test.}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=0.8\textwidth]{aggcluster_random.pdf}
		\caption{Examples of a given hierarchy and its “twin”.}
	\end{figure}
\end{frame}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
	\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
	\caption{Average ranks and 95\% confidence intervals for natural hierarchy and its 100 twins, tourism dataset (left) and mortality dataset(right).}
\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
		\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
		\caption{Average ranks and 95\% confidence intervals for the best cluster hierarchy and its 100 twins, tourism dataset (left) and mortality dataset(right).}
	\end{figure}

@@

\begin{frame}{Forecast combination}
	\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/tourism/P4_benchmarks_h12.pdf}
	\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/mortality/P4_benchmarks_h12.pdf}
	\caption{Average ranks and 95\% confidence intervals for all approaches on tourism dataset(left) and mortality dataset(right) based on MCB test}
	\end{figure}
	\begin{itemize}
		\item On both datasets, forecast combination improves forecast performance compared to any single hierarchy. The improvement on the mortality dataset is more pronounced.
	\end{itemize}
\end{frame}

@@

		\item[] \small\color{purple}Homepage: {\color{blue}   \url{https://bohan-zhang.com}}
            \item[] \small\color{purple}Paper on arXiv: {\color{blue} \url{https://arxiv.org/abs/2404.06064}}

    \vspace{0.1cm}
  {\large\color{black} Vote for me on Whova, thanks!}

@@

\begin{frame}[noframenumbering]{References}
\footnotesize
\vspace{-0.02in}
	\bibliographystyle{agsm}
	\bibliography{R1/references.bib}		
\end{frame}
